Universal Anonymous Signatures

### 2022-06-03 prism-backend/research/gsac/app-building-blocks.tex
Upgrading definitions and proofs.

>>>>

\paragraph{Augmenting with NIZKs.} %
\todo{This is quite informal. Perhaps expand...} 
In the previous \SBCM scheme, it is straightforward to require that the party
running \SBCMCom proves some arbitrary claim over the messages to be signed
(both those in committed or plaintext form). This can be done by having this
party add a NIZK over the corresponding NP statement. We will be using this
extension, and use $\SBCM^{\NIZKRel}$ to denote such an \SBCM with proofs for
claims in \NIZKRel.

### 2022-06-03 prism-backend/research/gsac/construction-uas.tex
Upgrading definitions and proofs.

\begin{description}
\item[$\NIZKRel_{\Issue}$:] Set by issuers, governs via \fissue the rules for
  issuing new credentials. It is defined as $\NIZKRel_{\Issue} = \lbrace
  (\usk,\scred,\attrs_{\scred},r), (\Ccom,\attrs,\sipk_{\scred}): \Ccom =
  \CCommit(usk;r) \land \fissue(\usk,\scred,\attrs) = 1 \land \forall \cred \in
  \scred, \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1 \rbrace$,
  where for readability we write $\attrs_{\scred}$ as abbreviation for $\lbrace
  \attrs_{\cred} \rbrace_{\cred \in \scred}$, and similarly for $\sipk_{\scred}$.
  Basically, this relation requires that, in order to issue a credential with
  attribtes \attr, and bound to \usk, the requester has to commit to \usk and
  prove knowledge of it, as well as prove that all additional credentials needed
  for the issuing to be granted, meet some defined policy \fissue.
\item[$\NIZKRel_{\Sign}$:] Can be set by anyone but, for simplicity, assume
  verifiers define them. Governs via \feval and \finsp what utility
  information is directly revealed by signatures, or extracted by openers.
  It is defined as $\NIZKRel_{\Sign} = \lbrace (\usk,\scred,
  \attrs_{\scred},\yinsp,r),(\msg,\feval,\yeval,\Ec,\sipk_{\scred},\Eek): \Ec =
  \EEnc(\Eek,\yinsp;r) \land \yeval = \feval(\usk,\scred,\msg) \land
  \yinsp = \finsp(\yeval,\usk,\scred,\msg) \land \forall \cred \in \scred,
  \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1) \rbrace$, with
  $\attrs_{\scred}$ and $\sipk_{\scred}$ as in $\NIZKRel_{\Issue}$. In a
  nutshell, this relation ensures that signatures will produce the correct
  signature evaluation and opening values, and that any credential used to
  create the signature is bound to the same \usk key.
\item[$\NIZKRel_{\Open}$:] Ensures that the utility information extracted by
  the \Open algorithm is correct. It is defined as $\NIZKRel_{\Open} =
  \lbrace (\osk),(\Ec,\yinsp): \yinsp = \EDec(\osk,\Ec) \rbrace$.
\end{description}

@@

\paragraph{$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle\Obtain(\usk,\scred,\attrs),\Issue(\isk,\sipk,\attrs)\rangle$.} %
The protocol is run between an issuer, and a user with secret key \usk and
credentials \scred, where each $\cred \in \scred$ is issued by an issuer with
public key $\ipk_{\cred}$ (which we assume that the user can easily retrieve,
e.g., from secure storage, given \cred), and attests attributes
$\attrs_{\cred}$. The user requests a signature on a commitment to the user key,
as well as on the attributes in \attrs. In addition, the user proves that the
issuance function \fissue established by the issuer is satisfied by the
credentials in $\scred$
and its user secret key. For this, we use relation $\NIZKRel_{\Issue}$, as
defined above. The interactive protocol for a user to obtain a credential from
an issuer of the system is then simply an execution of the interactive signing
protocol of an \SBCM scheme, where the user runs $\SBCMCom(\ipk,\usk,\attrs)$,
and the issuer runs $\SBCMSign(\isk,\attrs)$; in both cases, using
$\NIZKRel_{\Issue}$ as \NIZK relation. The credential \cred produced by the user
is the result of the interactive signing protocol, and the \utrans entry for
the issuer is its transcript which is a $(\Ccom,\attrs,\sipk,\cred,\pi)$ tuple.

@@

\paragraph{$(\sig,\yeval) \gets \Sign(\usk,\opk,\scred,\msg,\feval)$.} %
In the signing algorithm, we make use of relation $\NIZKRel_{\Sign}$.
% 
From this, in order to produce a valid signature, the user first evaluates
$\yeval \gets \feval (\usk,\scred,\msg)$, and decides whether or not to continue
with the signing process -- this may depend, e.g., on the opening policy of
\opk, as the output of \feval may influence whether the user will be
de-anonymizable or not, depending on the \finsp function in \opk.
%
Then, the user parses \opk as $(\Svk,\Eek,\finsp,\sig_{\finsp})$ and checks that
$\Verify(\Svk,\sig_{\finsp},\finsp) = 1$ (note that this step may be cached), to
compute $\yinsp \gets \finsp(\yeval,\usk,\scred,\msg)$, and encrypt it with
\Eek by running $\Ec \gets \EEnc(\Eek,\yeval;r)$ for some fresh randomness $r$.
Finally, the user computes
$\NIZKproof \gets \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\usk,\scred,
\attrs_{\scred},\yinsp,r),(\msg,\feval,\yeval,\Ec,\sipk_{\scred},\Eek))$ and
outputs $(\sig = (\NIZKproof,\Ec),\yeval)$.

\paragraph{$1/0 \gets \Verify(\opk,\sipk,\sig,\yeval,\msg,\feval)$.} %
The ``cryptographic'' side of the verification essentially consists on checking
the NIZK proof. That is, parse \sig as $(\NIZKproof,\Ec)$ and check whether
$\NIZKVerify(\NIZKcrs,\NIZKproof,(\msg,\feval,\yeval,\Ec,\sipk,\opk)) = 1$. In
addition, the verifier may further check whether \yeval meets its needs.

\paragraph{$(\yinsp,\NIZKproof)/\bot \gets
  \Open(\osk,\sipk,\sig,\yeval,\msg,\feval)$.} %
Here we leverage relation $\NIZKRel_{\Open}$.
%
To open a signature, the opener first verifies the signature by running $\Verify
(\opk,\sipk, \sig,\yeval,\msg,\feval)$. If the verification succeeds, it parses
\sig as $(\NIZKproof,\Ec)$, decrypts \Ec by running $\yeval \gets \EDec(\osk,
\Ec)$, and computes $\NIZKproof_{\Open} \gets \NIZKProve^{\NIZKRel_{\Open}}
(\NIZKcrs_{\Open},\osk,(\Ec,\yinsp))$. It returns $(\yinsp,
\NIZKproof_{\Open})$.

\paragraph{$1/0 \gets \Judge(\opk,\yinsp,\NIZKproof,\sig,\yeval,\msg)$.} %
To assess the validity of an opening proof, first check the signature
by running $\Verify(\opk,\sipk, \sig,\yeval,\msg,\feval)$. If the check succeeds,
parse \sig as $((\cdot,\Ec),\cdot)$ and verify \NIZKproof with $\NIZKVerify
(\NIZKcrs_{\Open},\NIZKproof,(\Ec,\yinsp))$. Accept it the NIZK verification
passes, and reject otherwise.

>>>>

\begin{description}
\item[$\NIZKRel_{\Issue}$:] Set by issuers, governs via \fissue the rules for
  issuing new credentials. It is defined as $\NIZKRel_{\Issue} = \lbrace
  (\usk,\scred,\attrs_{\scred},r), (\Ccom,\attrs,\sipk_{\scred}): \Ccom =
  \CCommit(usk;r) \land \fissue(\usk,\scred,\attrs) = 1 \land \forall \cred \in
  \scred, \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1 \rbrace$,
  where for readability we write $\attrs_{\scred}$ as abbreviation for $\lbrace
  \attrs_{\cred} \rbrace_{\cred \in \scred}$, and similarly for $\sipk_{\scred}$.
  Basically, this relation requires that, in order to issue a credential with
  attribtes \attr, and bound to \usk, the requester has to commit to \usk and
  prove knowledge of it, as well as prove that all additional credentials needed
  for the issuing to be granted, meet some defined policy \fissue.
\item[$\NIZKRel_{\Sign}$:] Can be set by anyone but, for simplicity, assume
  verifiers define them. Governs via \feval and \finsp what utility
  information is directly revealed by signatures, or extracted by openers.
  It is defined as $\NIZKRel_{\Sign} = \lbrace (\usk,\scred,
  \attrs_{\scred},\yeval^1,\yinsp,r,r'),(\msg,\feval,\yeval^0,\ceval,\cinsp,
  \sipk_{\scred},\Eek): \ceval = \EEnc(\Eek,\yeval^1;r) \land \cinsp= \EEnc
  (\Eek,\yinsp;r') \land (\yeval^0,\yeval^1) = \feval(\usk,\scred,\msg) \land
  \yinsp = \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \land \forall \cred \in
  \scred, \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) = 1) \rbrace$,
  with $\attrs_{\scred}$ and $\sipk_{\scred}$ as in $\NIZKRel_{\Issue}$. In a
  nutshell, this relation ensures that signatures will produce the correct
  signature evaluation and opening values, and that any credential used to
  create the signature is bound to the same \usk key.
\item[$\NIZKRel_{\Open}$:] Ensures that the utility information extracted by
  the \Open algorithm is correct. It is defined as $\NIZKRel_{\Open} =
  \lbrace (\osk),(\Ec,\yinsp): \yinsp = \EDec(\osk,\Ec) \rbrace$.
\end{description}

@@

\paragraph{$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle\Obtain(\usk,\ipk,\scred,\attrs),\Issue(\isk,\sipk,\attrs)\rangle$.} %
The protocol is run between an issuer with key pair $(\ipk,\isk)$, and a user
with secret key \usk and credentials \scred, where each $\cred \in \scred$ is
issued by an issuer with
public key $\ipk_{\cred}$ (which we assume that the user can easily retrieve,
e.g., from secure storage, given \cred), and attests attributes
$\attrs_{\cred}$. The user requests a signature on a commitment to the user key,
as well as on the attributes in \attrs. In addition, the user proves that the
issuance function \fissue established by the issuer is satisfied by the
credentials in $\scred$
and its user secret key. For this, we use relation $\NIZKRel_{\Issue}$, as
defined above. The interactive protocol for a user to obtain a credential from
an issuer of the system is then simply an execution of the interactive signing
protocol of an \SBCM scheme, where the user runs $\SBCMCom(\ipk,\usk,\attrs)$,
and the issuer runs $\SBCMSign(\isk,\attrs)$; in both cases, using
$\NIZKRel_{\Issue}$ as \NIZK relation. The credential \cred produced by the user
is the result of the interactive signing protocol, and the \utrans entry for
the issuer is its transcript which is a $(\Ccom,\attrs,\sipk,\cred,\pi)$ tuple.

@@

\paragraph{$\Sig \gets \Sign(\usk,\opk,\scred,\msg,\feval)$.} %
In the signing algorithm, we make use of relation $\NIZKRel_{\Sign}$.
% 
From this, in order to produce a valid signature, the user first evaluates
$(\yeval^0,\yeval^1) \gets \feval (\usk,\scred,\msg)$, and decides whether or
not to continue with the signing process -- this may depend, e.g., on the
opening policy of \opk, as the output of \feval may influence whether the user
will be de-anonymizable or not, depending on the \finsp function in \opk.
%
Then, the user parses \opk as $(\Svk,\Eek,\finsp,\sig_{\finsp})$ and checks that
$\Verify(\Svk,\sig_{\finsp},\finsp) = 1$ (note that this step may be cached), to
compute $\yinsp \gets \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg)$, and
separately encrypts both $\yeval^1$ and \yinsp with \Eek by running
$\ceval \gets \EEnc(\Eek,\yeval^1;r)$ and $\cinsp \gets \EEnc(\Eek,\yeval^1;
r')$ for some fresh randomness $r,r'$. Finally, the user computes
$\NIZKproof \gets \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\usk,\scred,
\attrs_{\scred},\yeval^1,\yinsp,r),(\msg,\feval,\yeval^0,\ceval,\cinsp,
\sipk_{\scred},\Eek))$ and outputs $(\sig = (\NIZKproof,\cinsp),\yeval,
\ceval)$.

\paragraph{$1/0 \gets \Verify(\opk,\sipk,\Sig,\msg,\feval)$.} %
The ``cryptographic'' side of the verification essentially consists on checking
the NIZK proof. That is, parse \Sig as $(\sig = (\NIZKproof,\cinsp),\yeval,
\ceval)$ and check whether $\NIZKVerify(\NIZKcrs,\NIZKproof,(\msg,\feval,\yeval,
\ceval,\cinsp,\sipk,\opk)) = 1$. In addition, the verifier may further check
whether \yeval meets its needs.

\paragraph{$(\yinsp,\NIZKproof)/\bot \gets
  \Open(\osk,\sipk,\Sig,\msg,\feval)$.} %
Here we leverage relation $\NIZKRel_{\Open}$.
%
To open a signature, the opener first verifies the signature by running $\Verify
(\opk,\sipk, \Sig,\msg,\feval)$. If verification succeeds, it parses
\Sig as $(\sig=(\NIZKproof,\cinsp),\yeval,\ceval)$, decrypts \Ec by running $\yinsp
\gets \EDec(\osk,\cinsp)$, and computes $\NIZKproof_{\Open} \gets
\NIZKProve^{\NIZKRel_{\Open}}(\NIZKcrs_{\Open},\osk,(\cinsp,\yinsp))$. It
returns $(\yinsp,\NIZKproof_{\Open})$.

\paragraph{$1/0 \gets \Judge(\opk,\yinsp,\NIZKproof,\sig,\yeval,\msg)$.} %
To assess the validity of an opening proof, first check the signature
by running $\Verify(\opk,\sipk, \sig,\yeval,\msg,\feval)$. If the check succeeds,
parse \sig as $((\cdot,\cinsp),\cdot)$ and verify \NIZKproof with $\NIZKVerify
(\NIZKcrs_{\Open},\NIZKproof,(\cinsp,\yinsp))$. Accept it the NIZK
verification passes, and reject otherwise.
